### 2018-01-23 manuscript.rmd
changed Rudjakovia Sex and DMC to NA in data, and adjusted code to render them as Dioecious and 0

#Named vectors for variables
sex = cdata$Sex
names(sex) = rownames(cdata)

@@

#Descending mantle Canal SIMMAP Setup
desc_mantle_data = cdata[which(!is.na(cdata$Desc.Mantle.Canal)),]
desc_mantle = desc_mantle_data$Desc.Mantle.Canal
names(desc_mantle)=rownames(desc_mantle_data)
DescMantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(desc_mantle))))
make.simmap(DescMantleTree, desc_mantle, nsim = 100, message=FALSE) -> desc_mantle_sim
```

>>>>

#Named vectors for variables
sex = cdata$Sex
names(sex) = rownames(cdata)
sex[which(names(sex)=="Rudjakovia sp")] <- "Dioecious" #Modified for graphing purposes

@@

#Descending mantle Canal SIMMAP Setup
desc_mantle_data = cdata[which(!is.na(cdata$Desc.Mantle.Canal)),]
desc_mantle = desc_mantle_data$Desc.Mantle.Canal
names(desc_mantle)=rownames(desc_mantle_data)
desc_mantle[which(names(desc_mantle)=="Rudjakovia sp")] <- 0 #Modified for graphing purposes
DescMantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(desc_mantle))))
make.simmap(DescMantleTree, desc_mantle, nsim = 100, message=FALSE) -> desc_mantle_sim
```
